Industrial Best Practice

### 2015-03-22 ibp/ibp.tex
started impact ass

\title{Industrial Best Practice}

@@

\section{Plan and Roadmap, 5p}
As mentioned in Section 2, the effects mo ifications to APIs have on the platform’s ecosystem are explored as being negative. However, there are no existing systematic guidelines or framewor s that take the ecosystem into account for how to best modify an API. Our proposed process for creating such a framework will be can be seen in Figure \ref{fig:roadmap}. This is an initial version of the roadmap \cite{!!!roadmap}, and it is advised that it is updated dur ng the process. The main reason for this is that it is impo tant to adapt to changes in the market, and if new needs are identified, the strategy should be redesigned to meet them.

\subsection{Designing the Roadmap}
The roadmap was developed using the standard T-Plan process \cite{!!!roadmap}. As such, identifying the market need was done as a part of the initial step. Following that, the products and technology needed to fill that gap were identified. As a final step the dependencies and ordering of the identified activites were sorted out which resulted in the current version of the roadmap. An overview of the process used to create the roadmap can be seen in Table \ref{tab:proc}

\begin{table}[ht]
\centering
\begin{tabular}[ht]{|c|l|l|}
\hline
\textbf{\#} & \textbf{Phase} & \textbf{Description} \\
\hline
1 & External & Identify the market needs \\
\hline
2 & Products & Identify required studies \& frameworks \\
\hline
3 & Technology & Identify required knowledge \\
\hline
4 & Organize & Identify what pull factors require which push factors \\
\hline
\end{tabular}
\caption{Roadmap Design Process}
\label{tab:proc}
\end{table}

\subsection{Knowledge Development}
Since we have made the assessment that the market need will remain relatively stable, careful research is essential to be able to deliver a product that meets the market needs. The main way of performing the initial study, to be able to increase the knowledge, will be through studying the existing literature. The reason for this is that three fields (API design, software evolution and software ecoystems) are currently well-explored, but the correlation and relationship between them has not yet been identified. Therefore, these fields will be explored in literature and a set of ``best practices" will be gathered from each field.

@@

\url{http://www.webarchive.org.uk/wayback/archive/20140614222502/http://www.jisc.ac.uk/fundingopportunities/projectmanagement/planning/dissemination.aspx}

\section{Impact Assessment, 2p}

>>>>

%8.5 pages is 60% 14 pages, which is the max
\title{Industrial Best Practice}

@@

\section{Plan and Roadmap, 5p}
As mentioned in Section 2, the effects modifications to APIs have on the platform’s ecosystem are explored as being negative. However, there are no existing systematic guidelines or framework s that take the ecosystem into account for how to best modify an API. Our proposed process for creating such a framework will be can be seen in Figure \ref{fig:roadmap}. This is an initial version of the roadmap \cite{!!!roadmap}, and it is advised that it is updated during the process. The main reason for this is that it is important to adapt to changes in the market, and if new needs are identified, the strategy should be redesigned to meet them.

\subsection{Designing the Roadmap}
The roadmap was developed using the standard T-Plan process \cite{!!!roadmap}. As such, identifying the market need was done as a part of the initial step. Following that, the products and technology needed to fill that gap were identified. As a final step the dependencies and ordering of the identified activities were sorted out which resulted in the current version of the roadmap. An overview of the process used to create the roadmap can be seen in Table \ref{tab:proc}

\begin{table}[ht]
\centering
\begin{tabular}[ht]{|c|l|l|}
\hline
\textbf{\#} & \textbf{Phase} & \textbf{Description} \\
\hline
1 & External & Identify the market needs \\
\hline
2 & Products & Identify required studies \& frameworks \\
\hline
3 & Technology & Identify required knowledge \\
\hline
4 & Organise & Identify what pull factors require which push factors \\
\hline
\end{tabular}
\caption{Roadmap Design Process}
\label{tab:proc}
\end{table}

\subsection{Knowledge Development}
Since we have made the assessment that the market need will remain relatively stable, careful research is essential to be able to deliver a product that meets the market needs. The main way of performing the initial study, to be able to increase the knowledge, will be through studying the existing literature. The reason for this is that three fields (API design, software evolution and software ecosystems) are currently well-explored, but the correlation and relationship between them has not yet been identified. Therefore, these fields will be explored in literature and a set of ``best practices" will be gathered from each field.

@@

Research findings and products—What is going to be disseminated?

II.
End users—Who will apply it in practice?

III.
Dissemination partners—Individuals, organisations or networks through whom you can reach end users?

IV.
Communication—How you convey the research outcomes?

V.
Evaluation—How you determine what worked?

VI.
Dissemination work plan—Where you start?
\newpage

\section{Impact Assessment, 2p}
This section will describe the impact that our framework will have.

\subsection{Now}
The key impact of our new API framework would be that it would transform the way companies and organisations motivate their design decisions for APIs. Today's software engineering companies mainly take into account their own agendas, and APIs are commonly changes for refactoring reasons or to reduce complexity. The most important factor when designing or changing APIs is, however, the users of the API and their needs. In the recent years, this has been realised by the software engineering industry. This has lead to less deprecations in the code of the API users.

\subsection{Impact on Technology and State of the Art}
The next step that we propose the industry takes, is to weigh the needs of the whole ecosystem in the assessment when creating APIs. This would lead to a more homogeneous environment where API platforms and API users can change their code jointly, to reduce the risk of deprecating for example methods. The impact of this could even be that companies start changing and improving their APIs to help the ecosystem, and thus causing a domino effect in the ecosystem which can even spread to other ecosystems. Probable areas where this could have an especially great impact would be in the areas of web development APIs, since they are widely used by a great amount of users. Another reason that web APIs would be impacted is that very clear boundaries between the ecosystems exist. The toolchain in web development is usually referred to as a ``stack" which literally is a set of frameworks and APIs that you use together to develop your application.

\subsection{Impact on Society}
If companies start developing their APIs to fit the needs of ecosystems, it would not only have a great impact on these specific isolated environments; it would develop the whole software engineering industry. In modern software development, very few applications are written without the use of APIs, and this means if APIs become better; it can increase the performance of software development. It might be hard to

This would have an especially great impact in web development APIs or programming language APIs.

*The key difference is that changes to APIs will not only be motivated for internal reasons, but also to help develop the whole ecosystem 
*This means that companies can help develop the environment they are in, and if done on a large scale it will drastically develop the world of software.
